Polytope notes

### 2019-11-30 notes/polytope-notes.tex
Took a second pass of edits

  Now let us consider some cell $C \subseteq \simplex$.
  Let $A$ be the affine span of the simplex, $A := \{p \in reals^n : \sum_y p_y = 1\}$.
  By existence of its $\H$-representation, we can represent the cell $C := \{p \in A : Bp \geq c\}$.
  In fact, we can set $c := \vec 0$ in order to enforce a unique representation of $B$, up to row reordering and scaling.
  \jessiet{Later: Talk about why $c = \vec 0$ and not some other vector.}

@@

@@

  	Then $\{p \in \simplex : \vec 0 \in \oplus_y p_y T_y\} = C$	if and only if non-simplex rows of $B$ appear in $E$ (possibly scaled) and every other row of $E$ is redundant with respect to $B$.
  	\btw{``replace prop 1 statement with `non-simplex rows of $B$ appear in $E$ (possible scaled) and every other row of $E$ is redundant with respect to $B$.'''}
  \end{proposition}
  \begin{proof}
	\begin{itemize}
		\item [$\implies$] First, assume $C = \{p \in \simplex: \vec 0 \in \oplus_y p_y T_y\}$.
		By Proposition~\ref{prop:relate-E-B}, we know that $C = D := \{p \in \simplex : Ep \geq \vec 0\}$.
		We can re-write $D$ as $\{p \in A : [E;I] p \geq \vec 0\}$, building simplex constraints into the inequality rather than the domain assumption.
		By the assumed equality, every row of $B$ must then appear in $[E;I]$, where $I$ is the $n$-element identity matrix.
		As $\{p \in A : I p \geq \vec 0\}$ strictly defines the simplex constraints, any non-simplex constraint of $B$ must then be described by a row of $E$, up to rescaling.

		What's more is that since the polytopes are the same, they have a unique minimal $\H$-representation (up to rescaling) since they are defined by an inequality on $\vec 0$.
		As $D$ is defined by distributions on the simplex and $C$ on the affine span of the simplex, and $\simplex \subset A$, we have the rest of the rows in $E$ necessarily being redundant with respect to $B$.  \jessie{revisit.}

		\item [$\impliedby$] Now, suppose that any non-simplex rows of $B$ appear in $E$, and every other row of $E$ is redundant with respect to $B$.
		By adding simplex constraints to the affine span of the simplex, we then have $\{p \in A : Bp \geq \vec 0\} = \{p \in A : [E; I] \geq \vec 0 \}$. \jessiet{Double check we can claim this at this point...}
		The latter set is equal to $D$ once we change the domain of $p$, so that we have $D = \{p \in \simplex : Ep \geq \vec 0\} = \{p \in A : [E;I] p \geq \vec 0\}$.

>>>>

  Now let us consider some cell $C \subseteq \simplex$.
  Let $A$ be the affine span of the simplex, $A := \{p \in \reals^n : \sum_y p_y = 1\}$.
  By existence of its $\H$-representation, we can represent the cell $C := \{p \in A : Bp \geq c\}$.
  In fact, we can set $c := \vec 0$ in order to enforce a unique representation of $B$, up to row reordering and scaling.
  This also allows us to use the same matrix for the $\H$-representation even as we scale the simplex by a positive constant.

@@

  \begin{definition}
  	\jessie{I don't like this definition, but I'm pretty sure it's correct at least.  Can we simplify it?}
  	We say a  row $X_i$ of the matrix $X$ is \emph{redundant} with respect to matrix $Y$ describing the polytope $P^Y := \{z \in A : Yz \geq \vec 0\}$ if we have $\{z \in P^Y : Xz \geq \vec 0\} = \{z \in P^Y : X^{-i}z \geq \vec 0\}$, where $X^{-i}$ is the matrix $X$ with the row $X_i$ removed.
  \end{definition}

@@

  	Then $\{p \in \simplex : \vec 0 \in \oplus_y p_y T_y\} = C$	if and only if non-simplex rows of $B$ appear in $E$ (possibly scaled) and every other row of $E$ is redundant with respect to $B$.
  	\btw{``replace prop 1 statement with `non-simplex rows of $B$ appear in $E$ (possible scaled) and every other row of $E$ is redundant with respect to $B$.'''}
  \end{proposition}
  \begin{proof}
	\begin{itemize}
		\item [$\implies$] First, assume $C = \{p \in \simplex: \vec 0 \in \oplus_y p_y T_y\}$.
		By Proposition~\ref{prop:relate-E-B}, we know that $C = D := \{p \in \simplex : Ep \geq \vec 0\}$.
		We can re-write $D$ as $\{p \in A : [E;I_n] p \geq \vec 0\}$, building simplex constraints into the inequality rather than the domain assumption.
		By the assumed equality, every row of $B$ must then appear in $[E;I_n]$, where $I_n$ is the $n$-element identity matrix.
		As $\{p \in A : I_n p \geq \vec 0\}$ strictly defines the simplex, any non-simplex constraint of $B$ must then be described by a row of $E$, up to rescaling.

		What's more is that since the polytopes are the same, they have a unique minimal $\H$-representation (up to rescaling) since they are defined by an inequality on $\vec 0$.
		As $D$ is defined by distributions on the simplex and $C$ on the affine span of the simplex, and $\simplex \subset A$, we have the rest of the rows in $E$ necessarily being redundant with respect to $B$.
		To see this, suppose there was a row of $E$ that was not redundant with respect to $B$.
		If such a row did not partition the simplex, it would necessarily be redundant by the restriction that $C \subseteq \simplex$.
		Thus, such a row much partition the simplex, but not appear in $B$ up to rescaling.
		Again, if the constraint does not partition the cell, the constraint is redundant, and if it does, then $C \neq D$, yielding a contradiction.

		\item [$\impliedby$] Now, suppose that any non-simplex rows of $B$ appear in $E$, and every other row of $E$ is redundant with respect to $B$.
		Then we have $D = \{p\in \simplex : Ep \geq \vec 0\} = \{p \in \simplex : Bp \geq \vec 0\}$ by the assumption and this polytope is equal to $\{p \in A : Bp \geq \vec 0\} = C$ since we require $C\subseteq \simplex$, so $B$ contains any non-redundant simplex constraints.
